---
title: "Post Live Session 8 - May 29th"
author: "Mike Martos"
date: "June 25, 2016"
output:
  html_document:
    keep_md: yes
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r libraries}
library(downloader)
library(ggplot2)
library(vcd)
```

###Download data 
```{r downloadData}
download("http://stat.columbia.edu/~rachel/datasets/nyt29.csv",
         destfile="./Data/Raw/clickstream29.csv")
clickstream29 <- read.csv("./Data/Raw/clickstream29.csv")
```

###Tidy data
```{r tidyData}
#Get min and max of age
min <- min(clickstream29$Age)
max <- max(clickstream29$Age)
#Create breaks
breaks <- c(min,18,24,34,44,54,64,max)
#Make the signed in a factor
clickstream29$Signed_In <- factor(clickstream29$Signed_In)
#Make the Gender in a factor
clickstream29$Gender <- factor(clickstream29$Gender)
#Make the Gender in a factor
clickstream29$CTR <- clickstream29$Clicks/clickstream29$Impressions
```

###Create new field for ageGroup and assign from breaks
```{r ageGroup}
clickstream29$ageGroup <- cut(clickstream29$Age, breaks, 
                              labels = c("18-", "18-24", "25-34", "35-44", "45-54", "55-64", "65+"), 
                              include.lowest = TRUE, ordered_result = TRUE)
```

###Create new field for CTRGroup and assign from breaks, intervals closed on the left
```{r CTRGroup}
#Create breaks
breaks <- c(0,0.2,0.4,0.6,0.8,1)
clickstream29$CTRGroup <- cut(clickstream29$CTR, breaks, 
                              labels = c("0.0-0.2", "0.2-0.4", "0.4-0.6", "0.6-0.8", "0.8-1.0"), 
                              include.lowest = TRUE, ordered_result = TRUE, right = FALSE)
```

###Get the total number of Male, Impressions, Clicks and Signed_In (0=Female, 1=Male)
```{r Counts}

```


###Remove some data and store in variables
```{r subsetData}
#Remove records with no ages
clickstream29Age <- subset(clickstream29, clickstream29$Age > 0)
#Subset records with clicks
clickstream29Click <- subset(clickstream29Age, clickstream29Age$Clicks > 0)
#Subset records with Impressions > 0
ImpSub <- subset(clickstream29, clickstream29$Impressions > 0)
```

###Store intermediate files
```{r storeFileageGroup}
write.csv(clickstream29, file = "./Data/ClickStream29ageGroup.csv")
write.csv(clickstream29Age, file = "./Data/ClickStream29ageGroupWithAge.csv")
write.csv(clickstream29Click, file = "./Data/ClickStream29ageGroupWithAgeClicks.csv")
write.csv(ImpSub, file = "./Data/ImpSub.csv")
```


###Plot distributions of number impressions and click-through-rate for the age groups, the problem here is that the EDA showed the age, gender are only recorded for Signed_in users, thus the users that were not signed in will have 0 age and will have 0 as gender, which is not correct.
```{r}
plot(ImpSub$ageGroup, ImpSub$CTR, main="Distribution CTR")

```

###Number or users registered as Male
```{r CountMale}
sum(ImpSub$Gender == 1)
```

###Summatory of number of impresions
```{r CountImpressions}
sum(ImpSub$Impressions)
```

###Summatory of number of clicks
```{r CountClick}
sum(ImpSub$Clicks)
```

###Number of users showing as signed in.
```{r CountSigned}
sum(ImpSub$Signed_In == 1)
```

###Mean of Age
```{r meanAge}
mean(ImpSub$Age)
```

###Mean of Impressions
```{r meanImpressions}
mean(ImpSub$Impressions)
```

###Mean of clicks
```{r meanClick}
mean(ImpSub$Clicks)
```

###Mean of CTR
```{r meanCTR}
mean(ImpSub$CTR)
```

###Mean of Percentage of males
```{r pctMale}
100 * sum(ImpSub$Gender == 1)/length(ImpSub$Gender)
```

###Mean of Percentage of Signed In
```{r pctSignedIn}
100 * sum(ImpSub$Signed_In == 1)/length(ImpSub$Gender)
```

###Mean of Impressions by AgeGroup
```{r meanImpressionAge}
aggregate(ImpSub[, 3], list(ImpSub$ageGroup), mean)
```

###Mean of clicks by AgeGroup
```{r meanClickAge}
aggregate(ImpSub[, 4], list(ImpSub$ageGroup), mean)
```

###Mean of CTR by AgeGroup
```{r meanCTRAge}
aggregate(ImpSub[, 6], list(ImpSub$ageGroup), mean)
```

###Percentage of Males by AgeGroup
```{r pctMaleAge}
sumAge <- aggregate(ImpSub$Gender == 1,list(ImpSub$ageGroup), sum)
lenAge <- aggregate(ImpSub[, 6], list(ImpSub$ageGroup), length)
merged <- merge(sumAge,lenAge,by="Group.1")
names(merged) <- c("ageGroup","MalesQty","TotalQty")
merged$pct <- round(100 * merged$MalesQty/merged$TotalQty,2)
merged
```

###Percentage of signed in by AgeGroup, again, only signed in, show gender, that is why we get these results
```{r pctSignedInAge}
meanSigned <- aggregate(ImpSub$Signed_In == 1,list(ImpSub$ageGroup), sum)
lenAge <- aggregate(ImpSub[, 6], list(ImpSub$ageGroup), length)
merged <- merge(meanSigned,lenAge,by="Group.1")
names(merged) <- c("ageGroup","SignedQty","TotalQty")
merged$pct <- round(100 * merged$SignedQty/merged$TotalQty,2)
merged
```

###Create a table of the CTRGroup vs AgeGroup counts
```{r ctrGroupVsageGroup}
table(ImpSub$CTRGroup, ImpSub$ageGroup)
```

###Plot distribution Impressions
```{r}
qplot(ImpSub$Impressions, main="Distribution Impressions", fill=ImpSub$ageGroup,binwidth = 0.5)

```

###Plot distribution CTR
```{r}
qplot(ImpSub$CTR, main="Distribution CTR", fill=ImpSub$ageGroup,binwidth = 0.05)

```

###As mentioned earlier, I found that only signed in users have real gender and age information recorded, the default age for that group of not signed user is 0, which shows in the previous two plots, give this I've decided to plot the last two graphics for only signed in users, for that I have Data.frame *clickstream29Age* which I calculated earlier in the process. **Note the change in the 18- group**
```{r AdditionalPlots}
qplot(Impressions, data=clickstream29Age, fill=ageGroup, 
      main="Impressions by Age Group, Signed In Only",binwidth = 0.5)

qplot(CTR, data=clickstream29Age, fill=ageGroup, 
      main="Impressions by Age Group, Signed In Only",binwidth = 0.05)


```



       